Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-22 ms.tex
complete rewrite of abstract, other minor edits

\begin{abstract}
We present full-sky, $6.1'$ resolution maps of dust optical depth and 
temperature derived by fitting the \cite{FDS99} two-component dust emission 
model to the \PLANCK~217, 353, 545, and 857 GHz maps along with  
\IRAS~100$\mu$m data. This parametrization of the far-infrared thermal dust 
spectrum as the sum of two modified blackbodies serves as an important 
alternative to the commonly adopted single modified blackbody dust emission 
model. Because our two-component model matches the dust spectrum near its 
peak, accounts for the flattening of the dust spectrum at millimeter 
wavelengths, and specifies dust temperature at 6.1$'$ FWHM, our model 
provides accurate, high-resolution thermal dust emission foreground predictions
from 100 GHz to 3000 GHz. We also calibrate the derived optical depth to 
reddening at visible wavelengths, and compare the resulting reddening estimates
with those based on stellar spectra, as well as those of \cite{SFD} and 
\cite{planckdust} based on infrared emission.

@@

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and \IRAS~100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative parametrization for the dust spectral energy distribution 
(SED) composed  of \PLANCK~and \IRAS~data. In doing so, we obtain maps of dust 
temperature and optical depth, both at $6.1'$ resolution. Because we employ a 
model that has been validated with FIRAS data down to sub-mm wavelengths, we 
expect our best-fit parameters to be useful in constructing high-resolution 
predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also measurements near the peak of the dust 
SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
derived optical depth map will serve as a useful cross-check for extinction 
estimates based directly upon optical observations of stars
\citep[e.g.][]{schlafly14} and as a baseline for next-generation dust 
extinction maps incorporating high-resolution, full-sky infrared data sets such
as \WISE~\citep{wright10, meisner14} and \AKARI.

In $\S$\ref{sec:data} we introduce the data used throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the \PLANCK~maps to 
isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we 
explain the dust emission model we apply to the \PLANCK~and \IRAS/DIRBE data. 
In $\S$\ref{sec:bpcorr}, we discuss the details of predicting 
\PLANCK~observations based on this dust model. In $\S$\ref{sec:global} we 
derive constraints on our model's global parameters based on the \PLANCK~High 
Frequency Instrument (HFI) maps. In $\S$\ref{sec:fitting} we detail the Markov 
chain Monte Carlo (MCMC) method with which we have estimated the spatially 
varying parameters of our model. In $\S$\ref{sec:ebv} we calibrate our derived 
optical depth to reddening at optical wavelengths. In $\S$\ref{sec:lofreq} we
evaluate the accuracy of our two-component thermal dust emission predictions 
from 100-217 GHz. In $\S$\ref{sec:release} we present the full-sky maps of dust
temperature and optical depth we have obtained, and conclude in 
$\S$\ref{sec:conclusion}.

@@

The following subsections detail the processing steps we have applied to 
isolate Galactic dust emission in the \PLANCK~maps in preparation for our joint
\PLANCK/\IRAS~SED fits. % reference fitting section at end of this sentence ?

@@

\begin{deluxetable*}{cccccc} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{table:offs} Planck/IRAS Map Properties \& Pre-processing} 
\tablehead{
\colhead{$\nu$ (GHz)} &
\colhead{Offset ($K_{CMB}$)} & 
\colhead{Dipole ($K_{CMB}$)} & 
\colhead{$n_{\nu}$} ($K_{CMB}$) &
\colhead{$c_{\nu}$} &
\colhead{FWHM ($'$)} 
}
\startdata
100  & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & 7.77$\times$10$^{-5}$ & 0.0054 & 9.66 \\
143  & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & 3.25$\times$10$^{-5}$ & 0.0054 & 7.27 \\
217  & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ & $-$1.40$\times$10$^{-5}$ & 4.51$\times$10$^{-5}$ & 0.0054 & 5.01 \\
353  & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ & $-$3.08$\times$10$^{-5}$ & 1.51$\times$10$^{-4}$ & 0.012  & 4.86 \\
     & Offset (MJy/sr)                                 & Dipole (MJy/sr)          & $n_{\nu}$ (MJy/sr)    &        &      \\ \cline{2-4} \\ [-2ex]
545  & 7.27$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$    & 0.046                 & 0.10   & 4.84 \\
857  & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ & -                        & 0.046                 & 0.10   & 4.63 \\
3000 & 0.0$\pm$4.3$\times$10$^{-2}$                    & -                        & 0.06                  & 0.10   & 6.1
\enddata
\end{deluxetable*}

>>>>

\begin{abstract}

We apply the \cite{FDS99} two-component thermal dust emission model to the
\PLANCK~HFI maps. This parametrization of the far-infrared dust spectrum as the
sum of two modified blackbodies serves as an important alternative to the 
commonly adopted single modified blackbody (MBB) dust emission model. Analyzing
the joint \PLANCK/DIRBE dust spectrum, we show that two-component models 
provide a better fit to the 100-3000 GHz emission than do single-MBB models, 
though by a lesser margin than found by \cite{FDS99} based on FIRAS and DIRBE. 
We also derive full-sky $6.1'$ resolution maps of dust optical depth and 
temperature by fitting the two-component model to the \PLANCK~217, 353, 545, 
and 857 GHz maps along with  DIRBE/\IRAS~100$\mu$m data. Because our 
two-component model matches the dust spectrum near its peak, accounts for the 
flattening of the dust spectrum at millimeter wavelengths, and specifies dust 
temperature at 6.1$'$ FWHM, our model provides reliable, high-resolution 
thermal dust emission foreground predictions from 100 GHz to 3000 GHz. We find 
that, in diffuse sky regions, our two-component 100-217 GHz thermal dust 
emission predictions are on average accurate to within $\le$2.2\%, which 
represents an improvement of 5-15\% relative to predictions based on the 
\cite{planckdust} single-MBB model. We calibrate our two-component optical 
depth to reddening at visible wavelengths, and compare the resulting reddening 
estimates with those based on stellar spectra. We find that imperfect zodiacal 
light subtraction is the dominant large-scale systematic problem in our 
two-component temperature map and reddening estimates.

@@

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and DIRBE/\IRAS~100$\mu$m emission with a 
single-MBB spectrum. Here we investigate the FDS99 two-component dust emission 
model as an alernative parametrization for the dust spectral energy 
distribution (SED) composed  of \PLANCK High Frequency Instrument (HFI), DIRBE 
and \IRAS~data. In doing so, we obtain maps of dust temperature and optical 
depth, both at $6.1'$ resolution. Because we employ a model that has been 
validated with FIRAS data down to submillimeter (submm) wavelengths, we expect 
our best-fit parameters to be useful in constructing high-resolution 
predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also measurements near the peak of the dust 
SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
derived optical depth map will serve as a valuable cross-check for extinction 
estimates based directly upon optical observations of stars 
\citep[e.g.][]{schlafly14} and as a baseline for next-generation dust 
extinction maps incorporating high-resolution, full-sky infrared data sets such
as \WISE~\citep{wright10, meisner14} and \AKARI.

In $\S$\ref{sec:data} we introduce the data used throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the \PLANCK~maps to 
isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we 
explain the two-component emission model we apply to the \PLANCK-based dust 
SED. In $\S$\ref{sec:bpcorr}, we discuss the details of predicting 
\PLANCK~observations based on this dust model. In $\S$\ref{sec:global} we 
derive constraints on our model's global parameters in light of the \PLANCK~HFI
maps. In $\S$\ref{sec:fitting} we detail the Markov chain Monte Carlo (MCMC) 
method with which we have estimated the spatially varying parameters of our 
model. In $\S$\ref{sec:ebv} we calibrate our derived optical depth to reddening
at optical wavelengths. In $\S$\ref{sec:lofreq} we evaluate the accuracy of our
two-component thermal dust emission predictions from 100-217 GHz. In 
$\S$\ref{sec:release} we present the full-sky maps of dust temperature and 
optical depth we have obtained, and conclude in $\S$\ref{sec:conclusion}.

@@

The following subsections detail the processing steps we have applied to 
isolate Galactic dust emission in the \PLANCK~maps in preparation for SED
fitting. % reference fitting section at end of this sentence ?

@@

\begin{deluxetable*}{cccccc} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{table:offs} Input Map Properties \& Pre-processing} 
\tablehead{
\colhead{$\nu$ (GHz)} &
\colhead{Offset ($K_{CMB}$)} & 
\colhead{Dipole ($K_{CMB}$)} & 
\colhead{$n_{\nu}$} ($K_{CMB}$) &
\colhead{$c_{\nu}$} &
\colhead{FWHM ($'$)} 
}
\startdata
100  & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & 7.77$\times$10$^{-5}$ & 0.0054 & 9.66 \\
143  & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & 3.25$\times$10$^{-5}$ & 0.0054 & 7.27 \\
217  & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ & $-$1.40$\times$10$^{-5}$ & 4.51$\times$10$^{-5}$ & 0.0054 & 5.01 \\
353  & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ & $-$3.08$\times$10$^{-5}$ & 1.51$\times$10$^{-4}$ & 0.012  & 4.86 \\
     & Offset (MJy/sr)                                 & Dipole (MJy/sr)          & $n_{\nu}$ (MJy/sr)    &        &      \\ \cline{2-4} \\ [-2ex]
545  & 7.27$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$    & 0.046                 & 0.10   & 4.84 \\
857  & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ & -                        & 0.046                 & 0.10   & 4.63 \\
3000 & 0.0$\pm$4.3$\times$10$^{-2}$                    & -                        & 0.06                  & 0.10   & 6.1
\enddata
\end{deluxetable*}
